method

### 2021-09-02 06_Paper/ER-ED/method.Rmd

# set top level directory to source file
here::i_am("flag_project_root_COGERED.txt")
```

@@

_Part three: ER choice._ <br>

>>>>

# set top level directory to source file
here::i_am("flag_project_root_CERED.txt")
```

@@

_Part three: ER choice._ <br>
After the discounting part, participants could choose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
Importantly, there were no further instruction, on what basis they should make their decision.
